```{r}
require(foreign)
require(ggplot2)
require(MASS)
require(Hmisc)
require(reshape2)
library(tidyverse)
library(brms)
```

```{r}
data <- readRDS("sentiment_df")
```

```{r}
scale_values <- function(x){(x-min(x))/(max(x)-min(x))}
data$SentimentGI <- scale_values(data$SentimentGI)
head(data)
```

```{r}
data$SentimentGI[data$SentimentGI == 0] <- 0.000001
data$SentimentGI[data$SentimentGI == 1] <- 0.999999
```

```{r}
data$rating = data$rating+1
data$rating <- factor(data$rating, ordered = TRUE)
```

```{r}
data$gender <- factor(data$gender, levels=c("female", "male"))
```

```{r}
rating_vs_gender <- brm(
  bf(rating ~ gender),
  data = data,
  family = cumulative(link = "logit")
)

summary(rating_vs_gender)
```

On average, women get lower ratings than men.

```{r}
conditional_effects(rating_vs_gender)
```

```{r}
gender_vs_sentiment <- brm(
  bf(gender ~ SentimentGI),
  data = data,
  family = bernoulli(link = "logit")
)

summary(gender_vs_sentiment)
```

Women's reviews are more likely to have lower sentiment scores than men's.

Lower sentiment score in reviews is predictive of the female author's gender, and higher sentiment score in reviews is predictive of the male author's gender.

```{r}
conditional_effects(gender_vs_sentiment)
```

```{r}
data$rating <- as.numeric(as.character(data$rating))
```

```{r}
es_vs_rating_gender <- brm(
  bf(SentimentGI ~ 0 + gender:rating),
  data = data,
  family = Beta(),
  #chains = 4, iter = 2000, warmup = 1000,
  #cores = 4, seed = 1234, 
  # Use the cmdstanr backend for Stan because it's faster and more modern than
  # the default rstan You need to install the cmdstanr package first
  # (https://mc-stan.org/cmdstanr/) and then run cmdstanr::install_cmdstan() to
  # install cmdstan on your computer.
  # backend = "cmdstanr",
  #file = "model_beta_bayes"  # Save this so it doesn't have to always rerun
)

summary(es_vs_rating_gender)
```

The sentiment decreases for female authors even the rating increases, whereas for male authors the sentiment increases as the rating increases.

```{r}
# TODO: make gender legend and rating on the x-axis
conditional_effects(es_vs_rating_gender)
```

```{r}
rating_vs_sentiment_gender <- brm(
  bf(rating ~ gender:SentimentGI),
  data = data,
  family = cumulative(link = "logit")
)

summary(rating_vs_sentiment_gender)
```

For men, there is a weak association of positive sentiment and higher ratings, but for women there’s no association.

```{r}
conditional_effects(rating_vs_sentiment_gender)
```
